Algomusicology, ????, Profit

### 2016-04-03 paper.tex
Fix a particularly egrarious overspill.
Set document to preprint.
Cite Champernowne.

% Based on the template for sigplanconf LaTeX Class by Paul C. Anagnostopoulos (paul@windfall.com)
\documentclass[numbers]{sigplanconf}

@@

@@

Fortunately, there are other transcendental numbers that are more predictable. The Champernowne constant has a
decimal expansion that is the concatenation of the digits of the natural numbers. To refer to the sequence of digits
in its decimal expansion we can simply refer to the Champernowne word.

@@

\bibitem{Overtone} Aaron, Sam and Rose, Jeff: Overtone (\url{http://overtone.github.io})
\bibitem{Anti EP} Autechre: Anti EP
\bibitem{Air on the G String} Wilhelmj, August arranging Bach, Johann Sebastian: Air on the G String
\bibitem{The Library of Babel} Borges, Jorge Luis: The Library of Babel
\bibitem{Gnomes} Brady, Pam, Parker, Trey and Stone, Matt. Episode 17, season 2 of South Park
\bibitem{Got to Give It Up} Got to Give It Up: Gaye, Marvin
\bibitem{Leipzig} Ford, Chris: Leipzig
\bibitem{Joseph Gallivan on pop} Gallivan, Joseph: Joseph Gallivan on pop (\url{http://www.independent.co.uk/life-style/jospeh-gallivan-on-pop-1414727.html})
\bibitem{Clojure} Hickey, Rich: Clojure
\bibitem{On Tables of Random Numbers}  Kolmogorov, Andrey: On Tables of Random Numbers
\bibitem{Midje} Marick, Brian: Midje
\bibitem{Analysis by Compression} Meredith, David: Analysis by Compression
\bibitem{USA Today} Oldenburg, Ann: 'Blurred Lines' jury finds for Marvin Gaye (\url{http://www.usatoday.com/story/life/music/2015/03/10/blurred-lines-trial-verdict/24492431/})
\bibitem{Contact} Sagan, Carl: Contact
\bibitem{Blurred Lines} Williams, Pharrel and Thicke, Robin: Blurred Lines

>>>>

% Based on the template for sigplanconf LaTeX Class by Paul C. Anagnostopoulos (paul@windfall.com)
\documentclass[numbers, preprint]{sigplanconf}

@@

\titlebanner{Submission for FARM 2016}

@@

Fortunately, there are other transcendental numbers that are more predictable. The Champernowne constant was discovered
by David Champernowne as an undergraduate\cite{The construction of decimals normal in the scale of ten}. It has a
decimal expansion that is the concatenation of the digits of the natural numbers. To refer to the sequence of digits
in its decimal expansion we can simply refer to the Champernowne word.

@@

\bibitem{Overtone} Aaron, Sam and Rose, Jeff: Overtone (\url{http://overtone.github.io})
\bibitem{Anti EP} Autechre: Anti EP
\bibitem{Air on the G String} Wilhelmj, August arranging Bach, Johann Sebastian: Air on the G String
\bibitem{The Library of Babel} Borges, Jorge Luis: The Library of Babel
\bibitem{The construction of decimals normal in the scale of ten} Champernowne, David: The construction of decimals normal in the scale of ten
\bibitem{Gnomes} Brady, Pam, Parker, Trey and Stone, Matt. Episode 17, season 2 of South Park
\bibitem{Got to Give It Up} Got to Give It Up: Gaye, Marvin
\bibitem{Leipzig} Ford, Chris: Leipzig
\bibitem{Joseph Gallivan on pop} Gallivan, Joseph: Joseph Gallivan on pop (\url{http://www.independent.co.uk/life-style/jospeh-gallivan-on-pop-1414727.html})
\bibitem{Clojure} Hickey, Rich: Clojure
\bibitem{On Tables of Random Numbers}  Kolmogorov, Andrey: On Tables of Random Numbers
\bibitem{Midje} Marick, Brian: Midje
\bibitem{Analysis by Compression} Meredith, David: Analysis by Compression
\bibitem{USA Today} Oldenburg, Ann: 'Blurred Lines' jury finds for Marvin Gaye (\url{http://www.usatoday.com/story/life/music/2015/03/10/blurred-lines-trial-verdict/24492431/})
\bibitem{Contact} Sagan, Carl: Contact
\bibitem{Blurred Lines} Williams, Pharrel and Thicke, Robin: Blurred Lines
